---
title: "Getting started with forkflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with forkflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
has_deps <- all(vapply(
  c("survival", "broom", "dplyr", "tidyr", "ggplot2"),
  requireNamespace, logical(1), quietly = TRUE
))
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = has_deps)
```

`forkflow` turns a space of defensible analytic choices into a single
reproducible object. This vignette runs a small multiverse on the `colon`
cancer trial that ships with the `survival` package, so it needs no download.

```{r pkgs, message = FALSE}
library(forkflow)
library(survival)
library(broom)
```

## 1. Prepare the cohort

```{r data}
d <- colon |>
  dplyr::filter(etype == 2) |>            # death endpoint
  tidyr::drop_na()
```

## 2. Enumerate the decision space

Every subset of the candidate adjusters is one defensible adjustment set.

```{r grid}
specs <- adjuster_sets(
  c("age", "sex", "obstruct", "perfor", "adhere", "differ", "surg")
)
nrow(specs)   # 2^7 = 128 specifications
```

## 3. Fit the whole grid

```{r fit}
results <- fit_multiverse(specs, function(spec) {
  f <- reformulate(c("node4", spec$adjusters[[1]]), "Surv(time, status)")
  coxph(f, data = d) |>
    tidy(conf.int = TRUE) |>
    dplyr::filter(term == "node4")
})
```

## 4. Summarise the vibration of effects

```{r voe}
voe(results)
```

## 5. Visualise

```{r plots, fig.width = 7, fig.height = 4.5}
spec_curve(results)
voe_volcano(results, colour = n_adjusters)
```

The relative ratio and the Janus fraction quantify how much the association for
`node4` depends on which covariates enter the model.
